An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2022-03-24 submissions/resubmission-ju-hofmann/ju-hofmann.tex
reorganize the folder

In this paper we present an open-source implementation of the algorithm
of the Congruent Matching Profile Segments (CMPS) method. \citet{cmps}
developed the CMPS method for ``objective comparison of striated tool
marks'' and demonstrated its use in some examples of comparing bullet
signature correlations. Although \citet{cmps} conceptually describe the
CMPS algorithm in their paper, the authors did not release an
implementation of their method. Thus, our effort here is to introduce
the CMPS method to the \texttt{R} \citep{R} community and provide an
open-source, publicly available implementation of the algorithm to use,
review, and improve. Our implementation is made available as part of the
\texttt{R} package \pkg{cmpsR} on GitHub at
\url{https://github.com/willju-wangqian/cmpsR}.

According to the Uniform Crime Reporting Program of FBI (Federal Bureau
of Investigation), ``more than 76 percent (76.7) of the homicides for
which the FBI received weapons data in 2020
\hh{is this really 2020 or should it be 2019?}involved the use of
firearms'', and the number of cases that involved the use of firearms in
2020 increased by close to 30 percent (29.3) compared to that in 2019
\citep{fbiucr}. Firearm examination could play an important role in all
these cases. An important task of firearm examination is to answer the
question of whether two pieces of evidence come from the same source or
whether a piece of evidence matches a sample obtained from a specific
firearm. Here, in particular, we are interested to determine whether two
bullets were fired from the same gun barrel. Assessing the similarity
between two bullets is based on a comparison of striation marks acquired
during the firing process as bullets are propelled through the barrel.
Current state of art sees firearms examiners make an assessment of
similarity based on a visual comparison, generally, using a comparison
microscope \citep{afte}. This practice has been criticized for its lack
of objectivity and the associated problem of determining valid error
rates \citep{pcast}.

A report published by the \citet{nrc} states that ``{[}m{]}uch forensic
evidence-including, for example, bite marks and firearm and toolmark
identification---is introduced in criminal trials without any meaningful
scientific validation, determination of error rates, or reliability
testing to explain the limits of the discipline.'' To overcome those
criticisms and concerns, researchers have been making an effort to build
databases and develop frameworks and algorithms that bring an objective
and quantitative assessment into the field. The database of
\citet{nistdb} with digital 3d topographic scans from various studies by
\citet{brundage}, \citet{hamby}, \citet{Hamby:2019} and others, provides
a great resource for researchers. Algorithms that can be validated and
tested and generate quantitative results are developed for 2D and 3D
surface texture \citep{song2005}, tool marks
\citep{ChumbleyL_Scott2010VoTM}, and striae on Land Engraved Areas
(LEAs) of bullets \citep[\citet{pmid30444940}, \citet{cmps}]{aoas}. The
notion of bullet signatures is one of the results of these efforts, and
we will use it to explain the CMPS algorithm and showcase the
\pkg{cmpsR} implementation. Bullet signatures can be extracted from
bullet land engraved areas (LEAs), typically one for each land engraved
area, and how those bullet signatures are extracted from scans will be
discussed in the Background section. Bullet signatures capture striation
marks on the bullet in a numeric format and therefore serve as the
foundation for algorithms. These scans played an important role in
bringing objectivity into the field. In the following sections we will:
review the background of bullet signature comparisons, discuss how we
followed the idea described by \citet{cmps} for the implementation of
the CMPS algorithm, propose new metrics based on the CMPS score and a
principled evaluation framework for algorithmic results comparison, and
present results of applying our implementation to real data.

@@

The datasets we worked with come from the James Hamby Consecutively
Rifled Ruger Barrel Study \citep{brundage, hamby, Hamby:2019}, in
particular, Hamby set 252 and Hamby set 44. For each Hamby set, a total
of 35 bullets is fired from (the same) ten consecutively manufactured
Ruger P-85 pistol barrels. Two bullets are fired from each barrel,
making up a set of 20 reference bullets. An additional 15 bullets are
fired from these ten barrels in a fashion unknown to the study
participant. The aim of the Hamby Study was to have firearms examiners
identify which barrel each of the 15 questioned bullets was fired from.
The Ruger P-85 barrels are traditionally rifled barrels with six grooves
and lands as shown in \autoref{fig:bullet}. During the firing process,
grooves and lands are engraved on a bullet. Firearms examiners use
striation marks on land engraved areas (LEAs) for their visual
comparison. For algorithmic purposes, 3D topographical images of land
engraved areas were obtained and stored in x3p format (XML 3-D Surface
Profile). The x3p format provides a standard way of exchanging 2D and 3D
profile data. It conforms to the ISO5436-2 standard
{[}\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}{]} adopted by the
OpenFMC (Open Forensic Metrology Consortium), a group of firearm
forensics researchers who contributes to the establishment of best
practices of using metrology in forensic science. Hamby set 252 was
scanned using a NanoFocus lens at 20x magnification with the scan
resolution being 1.5625 \textmu m \(\times\) 1.5625 \textmu m per pixel.
Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy
lab at Iowa State. These scans were acquired with a Sensofar Confocal
Light Microscope at 20x magnification for a nominal resolution of 0.645
\textmu m \(\times\) 0.645 \textmu m per pixel. Both Hamby set 252 and
Hamby set 44 are publicly available from the NIST Ballistics Database
Project \citep{nistdb}.

@@

\autoref{fig:process} gives an overview of all of the steps in the
process from scan to signatures. \autoref{fig:process}(a) shows a
rendering of a 3d scan of a bullet land engraved area. The raised
portion of the surface on the left and right of the scan are parts of
the adjacent groove engraved areas (GEAs), the middle area shows a
land-engraved area (LEA) with well expressed striation marks. The first
step of obtaining the bullet signature is to extract a cross-section at
a fixed height along the land engraving.

The thin white horizontal line in \autoref{fig:process}(a) indicates
which cross-section was identified by the algorithm to represent the
LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional
view. Groove engraved areas are removed from the analysis as indicated
by the vertical blue lines in \autoref{fig:process}(c) and
\autoref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess}
is fitted to capture the bullet curvature (\autoref{fig:process}(e))
and, finally, the \textbf{bullet signature} (\autoref{fig:process}(f))
is obtained as residuals of the cross-section and the fitted smooth.
Note, that in \citet{cmps} bullet signatures are referred to as bullet
profiles. However, to avoid confusion, we distinguish the notion of
bullet signatures from bullet profiles. Bullet profiles are shown in
panels (b), (c), and (d) of \autoref{fig:process}, while
\autoref{fig:process}(f) shows the corresponding bullet signature.
Identifying the groove engraved areas correctly is fundamental for a
correct down-stream analysis of the signatures. To allow for a
human-in-the middle inspection and intervention we have provided an
interactive web-application, implemented as \texttt{R} Shiny App
\citep{shiny}, \pkg{bulletinspectR} to identify and correct those
errors. An example of the extraction process with corresponding code and
parameter settings can be found on Github at
\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
Note that the process of extracting signatures might be different from
the one used in \citet{cmps} because no code or parameter settings are
made available publicly.

@@

\caption[A framework of obtaining a bullet signature]{A framework of obtaining a bullet signature. (a) rendering from the 3d topographic scan of a land engraved area (LEA). The selected crosscut location is indicated by a thin white horizontal line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained}\label{fig:process}
\end{figure}
\end{Schunk}

@@

Most algorithms for comparing striation marks are based on the digitized
signatures and produce a similarity score
\citep[\citet{ChumbleyL_Scott2010VoTM}, \citet{aoas},
\citet{pmid30444940}]{song2005}. The congruent matching profile segments
(CMPS) algorithm, developed by \citet{cmps} for ``objective comparison
of striated tool marks'', is one such algorithm. The algorithm's main
idea is to take a set of consecutive and non-overlapping basis segments
from the comparison and for each segment find the ``best'' registration
position on the reference (the other bullet signature) with respect to
their cross-correlation values. From a comparison of these registration
positions, a \textbf{congruent registration position} is identified, and
the number of basis segments taking the congruent registration position
is the CMPS score. Note that researchers in \citet{cmps} refer to the
origin of basis segments as the reference, but in this paper we refer to
it as the comparison signature. High CMPS scores are achieved between
more similar signatures and are therefore indicative of a same-source
pair. Low scores between pairs of signatures are attributed to different
source pairs. However, a specific threshold of the CMPS score to
distinguish between same-source and different-source comparisons is not
provided in \citet{cmps}, instead the threshold depends on the
underlying structure of the data and the choice of parameters. In a
legal setting this variability is problematic because it allows for
situations in which experts could choose parameters based on whether
they are witnesses for the defense or the prosecution. Further research
is needed to understand how to determine optimal threshold settings. The
CMPS algorithm can assist firearm examiners with drawing a conclusion
about the source of a comparison pair. Thus, in this paper we present an
open-source implementation of the CMPS algorithm in the R package
\pkg{cmpsR} available from Github
\url{https://github.com/willju-wangqian/cmpsR}. This publicly available
implementation calculates the CMPS score of a comparison using the
following code:

\begin{Schunk}
\begin{Sinput}
# install.packages("devtools") 
# devtools::install_github("willju-wangqian/CMPS")

@@

The \pkg{cmpsR} package is not publicly available from CRAN yet, and its
development version is available from Github and can be installed by

@@

In general, we assume each bullet has \(n\) land engravings (in our case
\(n=6\)). Let \(c_{ij}\) denote the CMPS score of a comparison between
bullet 1 land \(i\) and bullet 2 land \(j\), for \(i,j = 1, \dots, n\).
Let \(\mathcal{P}_k\) denote bullet land pairs in phase \(k\) for
\(k = 0, \dots, n-1\), and
\(\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}\),
where \(\mathbbm{1}_A\) denotes an indicator function. For example,
\(\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}\) when
\(n = 6\). Let \(k^*\) denote the index of the highest phase.

@@

\caption{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets. Land engraving pairs generated by the same land (KM comparisons) are highlighted. \hh{Note that in this example the axis along Bullet 2 starts with Land 2. This corresponds to Phase 2 in equation XXX}}\label{fig:tiles}
\end{figure}
\end{Schunk}

@@

As presented in the work of \citet{cmps}, researchers applied the CMPS
method to scans of one of the Hamby sets. While it is not explicitly
stated in the paper, we presume this to be Hamby 252, as only those
scans were publicly available at the time.
\hh{XXX Let's take out this statement once we hear back from NIST} In
order to show that our implementation of the CMPS algorithm is able to
reproduce the results in \citet{cmps} and be used for other data sets,
we applied our implementation to both Hamby set 252 and Hamby set 44.
For the purpose of reproducibility, we present how we obtained bullet
signatures from the Hamby set data and include code in the appendix: for
both Hamby 252 and Hamby 44, we started with scans in the form of x3p
files in the database. Following the framework proposed by \citet{aoas},
we used the same set of parameters, removed damaged bullet scans,
obtained bullet signatures for each bullet land engraving, and removed
outliers in bullet signatures. Note that researchers of \citet{cmps}
applied the CMPS algorithm to bullet signatures as well but used a
framework different from ours. However, since their work is not
open-source, we were not able to follow their framework and were only
able to reproduce the results for Hamby set 252 qualitatively.

@@

The code generating all results of this manuscript can be found on
Github at
\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}

@@

>>>>

In this paper we present an open-source implementation of the algorithm
of the Congruent Matching Profile Segments (CMPS) method. \citet{cmps}
developed the CMPS method for ``objective comparison of striated tool
marks'' and demonstrated its use in some examples of comparing bullet
signature correlations. Although \citet{cmps} conceptually describe the
CMPS algorithm in their paper, the authors did not release an
implementation of their method. Thus, our effort here is to introduce
the CMPS method to the \texttt{R} \citep{R} community and provide an
open-source, publicly available implementation of the algorithm to use,
review, and improve. Our implementation is made available as part of the
\texttt{R} package \pkg{cmpsR} on CRAN.

According to the Uniform Crime Reporting Program of FBI (Federal Bureau
of Investigation), ``more than 76 percent (76.7) of the homicides for
which the FBI received weapons data in 2020 involved the use of
firearms'' \citep{fbiucr}. At the same time, the number of murder
victims jumped between 2019 and 2020 by more than 23 percent (23.4) to
17754 \citep{fbiucr20}. This increase is unprecedented and highlights
the important role that firearm examination plays in all these cases. An
important task of firearm examination is to answer the question of
whether two pieces of evidence come from the same source or whether a
piece of evidence matches a sample obtained from a specific firearm.
Here, in particular, we are interested to determine whether two bullets
were fired from the same gun barrel. Assessing the similarity between
two bullets is based on a comparison of striation marks acquired during
the firing process as bullets are propelled through the barrel. Current
state of art sees firearms examiners make an assessment of similarity
based on a visual comparison, generally, using a comparison microscope
\citep{afte}. This practice has been criticized for its lack of
objectivity and the associated problem of determining valid error rates
\citep{pcast}.

A report published by the \citet{nrc} states that ``{[}m{]}uch forensic
evidence-including, for example, bite marks and firearm and toolmark
identification---is introduced in criminal trials without any meaningful
scientific validation, determination of error rates, or reliability
testing to explain the limits of the discipline.'' To overcome those
criticisms and concerns, researchers have been making an effort to build
databases and develop frameworks and algorithms that bring an objective
and quantitative assessment into the field. The database of
\citet{nistdb} with digital 3D topographic scans from various studies by
\citet{brundage}, \citet{hamby}, \citet{Hamby:2019} and others, provides
a great resource for researchers. Algorithms that can be validated and
tested and generate quantitative results are developed for 2D and 3D
surface texture \citep{song2005}, tool marks
\citep{ChumbleyL_Scott2010VoTM}, and striae on Land Engraved Areas
(LEAs) of bullets \citep[\citet{pmid30444940}, \citet{cmps}]{aoas}. The
notion of bullet signatures is one of the results of these efforts, and
we will use it to explain the CMPS algorithm and showcase the
\pkg{cmpsR} implementation. Bullet signatures can be extracted from
bullet land engraved areas (LEAs), typically one for each land engraved
area, and how those bullet signatures are extracted from scans will be
discussed in the Background section. Bullet signatures capture striation
marks on the bullet in a numeric format and therefore serve as the
foundation for algorithms. These scans played an important role in
bringing objectivity into the field. In the following sections we will:
review the background of bullet signature comparisons, discuss how we
followed the idea described by \citet{cmps} for the implementation of
the CMPS algorithm, propose new metrics based on the CMPS score and a
principled evaluation framework for algorithmic results comparison, and
present results of applying our implementation to real data.

@@

The datasets we worked with come from the James Hamby Consecutively
Rifled Ruger Barrel Study \citep{brundage, hamby, Hamby:2019}, in
particular, Hamby set 252 and Hamby set 44. For each Hamby set, a total
of 35 bullets is fired from (the same) ten consecutively manufactured
Ruger P-85 pistol barrels. Two bullets are fired from each barrel,
making up a set of 20 reference bullets. An additional 15 bullets are
fired from these ten barrels in a fashion unknown to the study
participant. The aim of the Hamby Study was to have firearms examiners
identify which barrel each of the 15 questioned bullets was fired from.
The Ruger P-85 barrels are traditionally rifled barrels with six grooves
and lands as shown in \autoref{fig:bullet}. During the firing process,
grooves and lands are engraved on a bullet. Firearms examiners use
striation marks on land engraved areas (LEAs) for their visual
comparison. For algorithmic purposes, 3D topographical images of land
engraved areas were obtained and stored in x3p format (XML 3-D Surface
Profile). The x3p format provides a standard way of exchanging 2D and 3D
profile data. It conforms to
\href{http://sourceforge.net/p/open-gps/mwiki/X3p/}{the ISO5436-2
standard} adopted by the OpenFMC (Open Forensic Metrology Consortium), a
group of firearm forensics researchers who contributes to the
establishment of best practices of using metrology in forensic science.
Hamby set 252 was scanned using a NanoFocus lens at 20x magnification
with the scan resolution being 1.5625 \textmu m \(\times\) 1.5625
\textmu m per pixel. Hamby set 44 was scanned at the Roy J Carver
High-Resolution microscopy lab at Iowa State. These scans were acquired
with a Sensofar Confocal Light Microscope at 20x magnification for a
nominal resolution of 0.645 \textmu m \(\times\) 0.645 \textmu m per
pixel. Both Hamby set 252 and Hamby set 44 are publicly available from
the NIST Ballistics Database Project \citep{nistdb}.

@@

\autoref{fig:process} gives an overview of all of the steps in the
process from scan to signatures. \autoref{fig:process}(a) shows a
rendering of a 3D scan of a bullet land engraved area. The raised
portion of the surface on the left and right of the scan are parts of
the adjacent groove engraved areas (GEAs), the middle area shows a
land-engraved area (LEA) with well expressed striation marks. The first
step of obtaining the bullet signature is to extract a cross-section at
a fixed height along the land engraving.

The thin white horizontal line in \autoref{fig:process}(a) indicates
which cross-section was identified by the algorithm to represent the
LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional
view. Groove engraved areas are removed from the analysis as indicated
by the vertical blue lines in \autoref{fig:process}(c) and
\autoref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess}
is fitted to capture the bullet curvature (\autoref{fig:process}(e))
and, finally, the \textbf{bullet signature} (\autoref{fig:process}(f))
is obtained as residuals of the cross-section and the fitted smooth.
Note, that in \citet{cmps} bullet signatures are referred to as bullet
profiles. However, to avoid confusion, we distinguish the notion of
bullet signatures from bullet profiles. Bullet profiles are shown in
panels (b), (c), and (d) of \autoref{fig:process}, while
\autoref{fig:process}(f) shows the corresponding bullet signature.
Identifying the groove engraved areas correctly is fundamental for a
correct down-stream analysis of the signatures. To allow for a
human-in-the middle inspection and intervention we have provided an
interactive web-application, implemented as \texttt{R} Shiny App
\citep{shiny}, \pkg{bulletinspectR} to identify and correct those
errors. An example of the extraction process with corresponding code and
parameter settings can be found in the ``Supplementary materials''. Note
that the process of extracting signatures might be different from the
one used in \citet{cmps} because no code or parameter settings are made
available publicly.

@@

\caption[A framework of obtaining a bullet signature]{A framework of obtaining a bullet signature. (a) rendering from the 3D topographic scan of a land engraved area (LEA). The selected crosscut location is indicated by a thin white horizontal line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained}\label{fig:process}
\end{figure}
\end{Schunk}

@@

Most algorithms for comparing striation marks are based on the digitized
signatures and produce a similarity score
\citep[\citet{ChumbleyL_Scott2010VoTM}, \citet{aoas},
\citet{pmid30444940}]{song2005}. The congruent matching profile segments
(CMPS) algorithm, developed by \citet{cmps} for ``objective comparison
of striated tool marks'', is one such algorithm. The algorithm's main
idea is to take a set of consecutive and non-overlapping basis segments
from the comparison and for each segment find the ``best'' registration
position on the reference (the other bullet signature) with respect to
their cross-correlation values. From a comparison of these registration
positions, a \textbf{congruent registration position} is identified, and
the number of basis segments taking the congruent registration position
is the CMPS score. Note that researchers in \citet{cmps} refer to the
origin of basis segments as the reference, but in this paper we refer to
it as the comparison signature. High CMPS scores are achieved between
more similar signatures and are therefore indicative of a same-source
pair. Low scores between pairs of signatures are attributed to different
source pairs. However, a specific threshold of the CMPS score to
distinguish between same-source and different-source comparisons is not
provided in \citet{cmps}, instead the threshold depends on the
underlying structure of the data and the choice of parameters. In a
legal setting this variability is problematic because it allows for
situations in which experts could choose parameters based on whether
they are witnesses for the defense or the prosecution. Further research
is needed to understand how to determine optimal threshold settings. The
CMPS algorithm can assist firearm examiners with drawing a conclusion
about the source of a comparison pair. Thus, in this paper we present an
open-source implementation of the CMPS algorithm in the R package
\pkg{cmpsR} available from both CRAN and Github. This publicly available
implementation calculates the CMPS score of a comparison using the
following code:

\begin{Schunk}
\begin{Sinput}
# install.packages("cmpsR")

@@

The \pkg{cmpsR} package is publicly available from CRAN and can be
installed by

\begin{Schunk}
\begin{Sinput}
install.packages("cmpsR") 
\end{Sinput}
\end{Schunk}

Moreover, its development version is also available from Github and can
be installed by

@@

In general, we assume each bullet has \(n\) land engravings (in our case
\(n=6\)). Let \(c_{ij}\) denote the CMPS score of a comparison between
bullet 1 land \(i\) and bullet 2 land \(j\), for \(i,j = 1, \dots, n\).
Let \(\mathcal{P}_k\) denote bullet land pairs in phase \(k\) for
\(k = 0, \dots, n-1\), and

\begin{align}
\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; \; j = (i + k) \;\mathrm{mod}\; n \}
\end{align}

, where \texttt{mod} denotes the modulo operation. For example,
\(\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}\) when
\(n = 6\). Let \(k^*\) denote the index of the highest phase.

@@

\caption[CMPS scores of all 36 pairwise bullet signature comparisons for two bullets]{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets. Land engraving pairs generated by the same land (KM comparisons) are highlighted. Note that in this example the axis along Bullet 2 starts with Land 2. This corresponds to Phase 1 in equation (1).}\label{fig:tiles}
\end{figure}
\end{Schunk}

@@

As presented in the work of \citet{cmps}, researchers applied the CMPS
method to scans of one of the Hamby sets. While it is not explicitly
stated in the paper, we presume this to be Hamby 252, as only those
scans were publicly available at the time. In order to show that our
implementation of the CMPS algorithm is able to reproduce the results in
\citet{cmps} and be used for other data sets, we applied our
implementation to both Hamby set 252 and Hamby set 44. For the purpose
of reproducibility, we present how we obtained bullet signatures from
the Hamby set data and include code in the appendix: for both Hamby 252
and Hamby 44, we started with scans in the form of x3p files in the
database. Following the framework proposed by \citet{aoas}, we used the
same set of parameters, removed damaged bullet scans, obtained bullet
signatures for each bullet land engraving, and removed outliers in
bullet signatures. Note that researchers of \citet{cmps} applied the
CMPS algorithm to bullet signatures as well but used a framework
different from ours. However, since their work is not open-source, we
were not able to follow their framework and were only able to reproduce
the results for Hamby set 252 qualitatively.

@@

For details about the implementation, examples and results, please refer
to the ``Supplementary materials''.

@@

\hypertarget{supplementary-materials}{%
\subsection{Supplementary materials}\label{supplementary-materials}}

The zip file ``supplementary-files.zip'' contains R scripts for
reproducing all aspects of this paper.

\textbf{Data not included in ``supplementary-files.zip''}

The processed data of Hamby set 252 and Hamby set 44 are stored in two
\texttt{.rds} files:

\begin{itemize}
\tightlist
\item
  \href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures252.rds}{\texttt{BulletSignatures252.rds}}
\item
  \href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures44.rds}{\texttt{BulletSignatures44.rds}}
\end{itemize}

And the ground truth of Hamby set 252 is provided in
\href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/StudyInfo.xlsx}{\texttt{StudyInfo.xlsx}}

Due to the size of the file, these processed data are not included in
the ``supplementary-files.zip'', but the links are provided for
download.

In order to reproduce the results in the paper, please download
``BulletSignatures252.rds'', ``BulletSignatures44.rds'', and
``StudyInfo.xlsx'' and save them in a folder named
``bullet\_signatures\_etc''. And place the folder
``bullet\_signatures\_etc'' into the folder of all the R scripts of
``supplementary-files.zip''.

Please check out the folder structure of
\href{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}{the
\texttt{reproducible} folder} for reference.

\textbf{File description}

\begin{itemize}
\tightlist
\item
  \texttt{hamby*\_result\_generator.R}: these R scripts take the
  processed data of Hamby set 252 and Hamby set 44, generate preliminary
  results used in the paper, and save the results in the \texttt{.csv}
  format in the folder \texttt{data-csv}.
\item
  \texttt{rds\_generator.R}: this R script takes the generated
  \texttt{.csv} files and produce \texttt{CMPSpaper\_results.rds}.
  \texttt{CMPSpaper\_results.rds} is identical to
  \texttt{data/CMPSpaper\_results.rds} and is used generate figures and
  other results presented in the paper.
\item
  \texttt{func\_collection.R}: this R script contains some helper
  functions used by other R scripts.
\end{itemize}

\textbf{Data included in ``supplementary-files.zip''}

\begin{itemize}
\tightlist
\item
  \texttt{data-csv}: this folder contains \texttt{.csv} files we
  generated using R scripts \texttt{hamby*\_result\_generator.R}
\item
  \texttt{CMPSpaper\_results.rds}: this is the \texttt{.rds} file we
  generated using R script \texttt{rds\_generator.R}
\end{itemize}

These data can be used as reference or example results of the
reproducible codes

\begin{itemize}
\tightlist
\item
  \texttt{csafe\_rf2.rds}: this \texttt{.rds} file contains the random
  forest model used in this paper
\end{itemize}
